Probabilistic Model of Bilateral Lymphatic Spread in Head and Neck Cancer

### 2024-06-11 _tex/manuscript.tex
Built site for gh-pages

>>>>

The distribution that marginalizes over the unknown midline extension
cases is shifted towards a lower prevalence. This makes intuitive sense:
With only six patients among the 65 with unknown midline extension
status, the upper bound for the prevalence has moved down compared to
six out of 29.

We chose to compare our model against such corrected prevalence
posteriors, because the model, too, is capable of marginalizing over
unknown midline extension in the data. It would therefore be inaccurate
to compare the model trained with the full dataset to only that part of
the patient cohort where the tumor lateralization was recorded.
